Evaluation of performances

### 2020-02-24 analysis/eval-performance.Rmd
wflow_publish(knitr_in("analysis/eval-performance.Rmd"), view = FALSE, verbose = TRUE)

R.utils::sourceDirectory("R")

# load drake objects
drake::loadd(
  bm_aggregated
)
library("mlr")
library("magrittr")
library("dplyr")
library("ggplot2")
library("ggrepel")
library("ggsci")
library("ggpubr")
library("ggbeeswarm")
library("flextable")
library("xtable")
```

```{r}
df_perf <- getBMRPerformances(bm_aggregated, as.df = T) %>%
  mutate(task.id = recode_factor(task.id,
    `defoliation-all-plots-HR` = "HR",
    `defoliation-all-plots-VI` = "VI",
    `defoliation-all-plots-NRI` = "NRI",
    `defoliation-all-plots-HR-NRI` = "HR-NRI",
    `defoliation-all-plots-HR-VI` = "HR-VI",
    `defoliation-all-plots-HR-NRI-VI` = "HR-NRI-VI",
  )) %>%
  tidyr::separate(learner.id, c("learner_group", "filter"),
    remove = FALSE,
    sep = " "
  )
```

@@

```{r eval-performance-1, warning=FALSE}
table1 <- df_perf %>%
  group_by(learner.id, task.id, filter) %>%
  slice(which.min(rmse_aggr)) %>%
  dplyr::rename(
    "Model" = learner_group,
    "Learner ID" = learner.id,
    "Task" = task.id,
    "Filter" = filter,
    "RMSE" = rmse_aggr,
    "SE" = se,
  ) %>%
  ungroup() %>%
  mutate(Filter = replace(Filter, is.na(Filter), "No Filter")) %>%
  select(-iter, -`Learner ID`, -rsq, -expvar) %>%
  arrange(RMSE)

# save as latex table
table1 %>%
  ungroup() %>%
  arrange(RMSE) %>%
  slice(1:15) %>%
  xtable(
    type = "latex",
    caption = "Top 15 results for any task/learner/filter combination, sorted by performance.",
    label = "tab:perf-top-15"
  ) %>%
  print(
    file = "code/98-paper/ieee/performance-top-20.tex",
    include.rownames = TRUE,
    latex.environments = c("center"),
    table.placement = "ht!",
    caption.placement = "top",
    timestamp = NULL
  )

saveRDS(table1, "code/98-paper/presentation/table-perf.rda")

@@

```{r eval-performance-2, warning=FALSE}
table2 <- df_perf %>%
  group_by(learner_group) %>%
  slice(which.min(rmse_aggr)) %>%
  mutate(filter = replace(filter, is.na(filter), "No Filter")) %>%
  arrange(rmse_aggr) %>%
  dplyr::rename(
    "Model" = learner_group,
    "Learner ID" = learner.id,
    "Task" = task.id,
    "Filter" = filter,
    "RMSE" = rmse_aggr,
    "SE" = se,
  ) %>%
  select(-rsq, -expvar, -iter) %>%
  select(-`Learner ID`)

# save as latex table
table2 %>%
  xtable(
    type = "latex",
    caption = "Best performance of each learner across any task and filter method.",
    label = "tab:best-learner-perf"
  ) %>%
  print(
    file = "code/98-paper/ieee/performance-best-per-learner.tex",
    include.rownames = TRUE,
    latex.environments = c("center"),
    table.placement = "ht!",
    scalebox = 0.90,
    caption.placement = "top",
    timestamp = NULL
  )

saveRDS(table2, "code/98-paper/presentation/table-best-learner-per-task.rda")

@@

results_aggr %>%
  ggplot(aes(x = rmse_aggr, y = task.id)) +
  # geom_jitter(aes(color = learner_group), size = 2, width = 0, height = 0.3) +
  # geom_dotplot(aes(fill = learner_group), binaxis="y",
  #                        stackdir="up") +
  geom_beeswarm(groupOnX = FALSE, aes(color = learner_group), size = 3) +
  scale_color_nejm(breaks = sort(levels(results_aggr$learner_group))) +
  labs(x = "RMSE", y = "Task", color = "Learner") +
  guides(size = FALSE) +
  scale_x_continuous(limits = c(30, 70)) +
  geom_label_repel(
    # subset data to remove out of bounds values
    data = results_aggr[results_aggr$rmse_aggr < 100, ],
    # from ggbeeswarm, avoid overlapping of points by labels
    position = position_quasirandom(),
    aes(label = paste0(filter, ",", round(rmse_aggr, 2))),
    size = 2.8,
    min.segment.length = 0.1,
    seed = 123,
    point.padding = 0.5
  ) +
  theme_pubr() +
  theme(
    panel.grid.major.y = element_line(size = 0.1, linetype = "dashed"),
    axis.title.y = element_blank(),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 12),
    axis.text.y = element_text(angle = 45),
    plot.margin = unit(c(6, 6, 6, 0), "pt")
  )
```

@@

@@

best_no_filter <- df_perf %>%
  mutate(task.id = recode_factor(task.id,
    `defoliation-all-plots-HR` = "HR",
    `defoliation-all-plots-VI` = "VI",
    `defoliation-all-plots-NRI` = "NRI",
    `defoliation-all-plots-HR-NRI` = "HR-NRI",
    `defoliation-all-plots-HR-VI` = "HR-VI",
    `defoliation-all-plots-HR-NRI-VI` = "HR-NRI-VI",
  )) %>%
  tidyr::separate(learner.id, c("learner_group", "filter"),
    remove = FALSE,
    sep = " "
  ) %>%
  mutate(filter = replace(filter, is.na(filter), "No Filter")) %>%
  dplyr::filter(filter == "No Filter") %>%
  group_by(learner_group, task.id) %>%
  dplyr::filter(learner_group == "SVM" | learner_group == "RF" | learner_group == "XGBoost") %>%
  slice(which.min(rmse_aggr))

@@

comb %>%
  ggplot(aes(x = rmse_aggr, y = learner_group)) +
  geom_beeswarm(groupOnX = FALSE, aes(color = filter), size = 3) +
  facet_wrap(~task.id) +
  # scale_color_nejm() +
  labs(x = "RMSE", y = "Task", color = "Filter") +
  guides(size = FALSE) +
  scale_x_continuous(limits = c(30, 50)) +
  theme_pubr() +
  theme(
    panel.grid.major.y = element_line(size = 0.1, linetype = "dashed"),
    axis.title.y = element_blank(),
    axis.text.y = element_text(angle = 45),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 12),
    plot.margin = unit(c(6, 6, 6, 0), "pt")
  )
```

@@

comb_borda %>%
  ggplot(aes(x = rmse_aggr, y = learner_group)) +
  geom_beeswarm(groupOnX = FALSE, aes(color = filter), size = 3) +
  facet_wrap(~task.id) +
  scale_color_nejm() +
  labs(x = "RMSE", y = "Task", color = "Filter") +
  guides(size = FALSE) +
  scale_x_continuous(limits = c(30, 50)) +
  theme_pubr() +
  theme(
    panel.grid.major.y = element_line(size = 0.1, linetype = "dashed"),
    axis.title.y = element_blank(),
    axis.text.y = element_text(angle = 45),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 12),
    plot.margin = unit(c(6, 6, 6, 0), "pt")
  )
```

@@

```{r filter-effect-all-vs-no-filter, warning=FALSE, dev = c("png", "pdf")}
results_aggr1 <- df_perf %>%
  filter(learner_group != "Ridge-MBO", learner_group != "Ridge-CV") %>%
  filter(learner_group != "Lasso-MBO", learner_group != "Lasso-CV") %>%
  mutate(filter = replace(filter, is.na(filter), "NF")) %>%
  mutate(learner_group = as.factor(learner_group)) %>%
  mutate(learner_group = recode(learner_group, `XGBoost` = "XG")) %>%
  group_by(learner_group, task.id, filter) %>%
  # we actually took the mean already in chunk 'aggr-perf'. This is only to get
  # summarise() working
  summarise(perf = mean(rmse_aggr))

results_aggr1 %>%
  ggplot(aes(x = perf, y = learner_group)) +
  geom_beeswarm(
    data = results_aggr1[results_aggr1$filter != "NF", ], size = 1.1, shape = 3,
    groupOnX = FALSE, aes(color = "Filter")
  ) +
  geom_point(
    data = results_aggr1[results_aggr1$filter == "NF", ],
    size = 2, shape = 19, aes(color = "No Filter")
  ) +
  facet_wrap(~task.id) +
  scale_color_nejm() +
  labs(x = "RMSE", y = "Task", colour = NULL) +
  guides(size = FALSE) +
  scale_x_continuous(limits = c(30, 50)) +
  theme_pubr() +
  theme(
    panel.grid.major.y = element_line(size = 0.1, linetype = "dashed"),
    axis.title.y = element_blank(),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 12),
  )
```

@@

```{r filter-effect-all-vs-borda-filter, warning=FALSE, dev = c("png", "pdf")}
results_aggr2 <- df_perf %>%
  na.omit() %>%
  filter(learner_group != "Ridge-MBO", learner_group != "Ridge-CV") %>%
  filter(learner_group != "Lasso-MBO", learner_group != "Lasso-CV") %>%
  mutate(learner_group = recode_factor(learner_group, `XGBoost` = "XG")) %>%
  group_by(learner_group, task.id, filter) %>%
  # we actually took the mean already in chunk 'aggr-perf'. This is only to get
  # summarise() working
  summarise(perf = mean(rmse_aggr))

results_aggr2 %>%
  ggplot(aes(x = perf, y = learner_group)) +
  geom_beeswarm(
    data = results_aggr2[results_aggr2$filter != "Borda", ],
    shape = 3, size = 1.1, aes(color = "Simple Filter"),
    groupOnX = FALSE
  ) +
  geom_point(
    data = results_aggr2[results_aggr2$filter == "Borda", ],
    shape = 19, size = 2, aes(color = "Borda Filter")
  ) +
  facet_wrap(~task.id) +
  scale_color_nejm() +
  labs(x = "RMSE", y = "Task", colour = NULL) +
  guides(size = FALSE) +
  scale_x_continuous(limits = c(30, 48)) +
  theme_pubr() +
  theme(
    panel.grid.major.y = element_line(size = 0.1, linetype = "dashed"),
    axis.title.y = element_blank(),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 12),
  )
```

>>>>

source(here::here("code/99-packages.R"))
load_packages()

# load drake objects
loadd(
  bm_aggregated_new
)
library("xtable")
library("flextable")
library("ggbeeswarm")
library("ggsci")
library("ggrepel")
library("ggpubr")
```

```{r}
df_perf <- getBMRPerformances(bm_aggregated_new, as.df = T) %>%
  mutate(task.id = recode_factor(task.id,
    `hr` = "HR",
    `vi` = "VI",
    `nri` = "NRI",
    `nri_vi` = "NRI_VI",
    `hr_nri` = "HR-NRI",
    `hr_vi` = "HR-VI",
    `hr_nri_vi` = "HR-NRI-VI",
  )) %>%
  tidyr::separate(learner.id, c("learner_group", "filter"),
    remove = FALSE,
    sep = " MBO "
  )
```

@@

```{r eval-performance-1, warning=FALSE}
table1 <- df_perf %>%
  group_by(learner.id, task.id, filter) %>%
  slice(which.min(rmse_aggr)) %>%
  dplyr::rename(
    "Model" = learner_group,
    "Learner ID" = learner.id,
    "Task" = task.id,
    "Filter" = filter,
    "RMSE" = rmse_aggr,
    "SE" = se,
  ) %>%
  ungroup() %>%
  mutate(Filter = replace(Filter, is.na(Filter), "No Filter")) %>%
  select(-iter, -`Learner ID`) %>%
  arrange(RMSE)

# save as latex table
table1 %>%
  ungroup() %>%
  arrange(RMSE) %>%
  slice(1:15) %>%
  xtable(
    type = "latex",
    caption = "Top 15 results for any task/learner/filter combination, sorted by performance.",
    label = "tab:perf-top-15"
  ) %>%
  print(
    file = "docs/00-manuscripts/ieee/performance-top-20.tex",
    include.rownames = TRUE,
    latex.environments = c("center"),
    table.placement = "ht!",
    caption.placement = "top",
    timestamp = NULL
  )

saveRDS(table1, "docs/00-manuscripts/presentation/table-perf.rda")

@@

```{r eval-performance-2, warning=FALSE}
table2 <- df_perf %>%
  group_by(learner_group) %>%
  slice(which.min(rmse_aggr)) %>%
  mutate(filter = replace(filter, is.na(filter), "No Filter")) %>%
  arrange(rmse_aggr) %>%
  dplyr::rename(
    "Model" = learner_group,
    "Learner ID" = learner.id,
    "Task" = task.id,
    "Filter" = filter,
    "RMSE" = rmse_aggr,
    "SE" = se,
  ) %>%
  select(-iter) %>%
  select(-`Learner ID`)

# save as latex table
table2 %>%
  xtable(
    type = "latex",
    caption = "Best performance of each learner across any task and filter method.",
    label = "tab:best-learner-perf"
  ) %>%
  print(
    file = "docs/00-manuscripts/ieee/performance-best-per-learner.tex",
    include.rownames = TRUE,
    latex.environments = c("center"),
    table.placement = "ht!",
    scalebox = 0.90,
    caption.placement = "top",
    timestamp = NULL
  )

saveRDS(table2, "docs/00-manuscripts/ieee/presentation/table-best-learner-per-task.rda")

@@

results_aggr %>%
  ggplot(aes(x = rmse_aggr, y = task.id)) +
  # geom_jitter(aes(color = learner_group), size = 2, width = 0, height = 0.3) +
  # geom_dotplot(aes(fill = learner_group), binaxis="y",
  #                        stackdir="up") +
  geom_beeswarm(groupOnX = FALSE, aes(color = learner_group), size = 3) +
  scale_color_nejm(breaks = sort(levels(results_aggr$learner_group))) +
  labs(x = "RMSE", y = "Task", color = "Learner") +
  guides(size = FALSE) +
  scale_x_continuous(limits = c(27, 47)) +
  geom_label_repel(
    # subset data to remove out of bounds values
    data = results_aggr[results_aggr$rmse_aggr < 100, ],
    # from ggbeeswarm, avoid overlapping of points by labels
    position = position_quasirandom(),
    aes(label = paste0(filter, ",", round(rmse_aggr, 2))),
    size = 2.8,
    min.segment.length = 0.1,
    seed = 123,
    point.padding = 0.5
  ) +
  theme_pubr() +
  theme(
    panel.grid.major.y = element_line(size = 0.1, linetype = "dashed"),
    axis.title.y = element_blank(),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 12),
    axis.text.y = element_text(angle = 45),
    plot.margin = unit(c(6, 6, 6, 0), "pt")
  )
```

@@

**DEPRECATED**: Please see the scatterplots below for a better visulization

@@

best_no_filter <- df_perf %>%
  mutate(task.id = recode_factor(task.id,
    `hr` = "HR",
    `vi` = "VI",
    `nri` = "NRI",
    `nri_vi` = "NRI_VI",
    `hr_nri` = "HR-NRI",
    `hr_vi` = "HR-VI",
    `hr_nri_vi` = "HR-NRI-VI",
  )) %>%
  tidyr::separate(learner.id, c("learner_group", "filter"),
    remove = FALSE,
    sep = " MBO "
  ) %>%
  mutate(filter = replace(filter, is.na(filter), "No Filter")) %>%
  dplyr::filter(filter == "No Filter") %>%
  group_by(learner_group, task.id) %>%
  dplyr::filter(learner_group == "SVM" | learner_group == "RF" | learner_group == "XGBoost") %>%
  slice(which.min(rmse_aggr))

@@

comb %>%
  ggplot(aes(x = rmse_aggr, y = learner_group)) +
  geom_beeswarm(groupOnX = FALSE, aes(color = filter), size = 3) +
  facet_wrap(~task.id) +
  # scale_color_nejm() +
  labs(x = "RMSE", y = "Task", color = "Filter") +
  guides(size = FALSE) +
  scale_x_continuous(limits = c(27, 47)) +
  theme_pubr() +
  theme(
    panel.grid.major.y = element_line(size = 0.1, linetype = "dashed"),
    axis.title.y = element_blank(),
    axis.text.y = element_text(angle = 45),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 12),
    plot.margin = unit(c(6, 6, 6, 0), "pt")
  )
```

@@

comb_borda %>%
  ggplot(aes(x = rmse_aggr, y = learner_group)) +
  geom_beeswarm(groupOnX = FALSE, aes(color = filter), size = 3) +
  facet_wrap(~task.id) +
  scale_color_nejm() +
  labs(x = "RMSE", y = "Task", color = "Filter") +
  guides(size = FALSE) +
  scale_x_continuous(limits = c(27, 47)) +
  theme_pubr() +
  theme(
    panel.grid.major.y = element_line(size = 0.1, linetype = "dashed"),
    axis.title.y = element_blank(),
    axis.text.y = element_text(angle = 45),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 12),
    plot.margin = unit(c(6, 6, 6, 0), "pt")
  )
```

@@

```{r filter-effect-all-vs-no-filter, warning=FALSE, dev = c("png", "pdf")}
results_aggr1 <- df_perf %>%
  filter(learner_group != "Ridge-CV") %>%
  filter(learner_group != "Lasso-CV") %>%
  # mutate(filter = replace(filter, "No Filter", "NF")) %>%
  mutate(learner_group = as.factor(learner_group)) %>%
  mutate(learner_group = recode(learner_group, `XGBoost` = "XG")) %>%
  mutate(filter = recode(filter, `No Filter` = "NF")) %>%
  mutate(learner_group = fct_rev(learner_group)) %>%
  group_by(learner_group, task.id, filter) %>%
  # we actually took the mean already in chunk 'aggr-perf'. This is only to get
  # summarise() working
  summarise(perf = mean(rmse_aggr))

results_aggr1 %>%
  ggplot(aes(x = perf, y = learner_group)) +
  geom_beeswarm(
    data = results_aggr1[results_aggr1$filter != "NF", ], size = 1.1, shape = 3,
    groupOnX = FALSE, aes(color = "Filter")
  ) +
  geom_point(
    data = results_aggr1[results_aggr1$filter == "NF", ],
    size = 2, shape = 19, aes(color = "No Filter")
  ) +
  facet_wrap(~task.id) +
  scale_color_nejm(guide = guide_legend(override.aes = list(shape = c(3, 19)))) +
  labs(x = "RMSE", y = "Task", colour = NULL) +
  guides(size = FALSE) +
  scale_x_continuous(limits = c(27, 51)) +
  theme_pubr() +
  theme(
    panel.grid.major.y = element_line(size = 0.1, linetype = "dashed"),
    axis.title.y = element_blank(),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 12),
  )
```

@@

```{r filter-effect-all-vs-borda-filter, warning=FALSE, dev = c("png", "pdf")}
results_aggr2 <- df_perf %>%
  na.omit() %>%
  filter(learner_group != "Ridge-CV") %>%
  filter(learner_group != "Lasso-CV") %>%
  mutate(learner_group = recode_factor(learner_group, `XGBoost` = "XG")) %>%
  group_by(learner_group, task.id, filter) %>%
  # we actually took the mean already in chunk 'aggr-perf'. This is only to get
  # summarise() working
  summarise(perf = mean(rmse_aggr)) %>% 
  ungroup()

results_aggr2 %>%
  ggplot(aes(x = perf, y = fct_reorder(learner_group, -perf))) +
  geom_beeswarm(
    data = results_aggr2[results_aggr2$filter != "Borda", ],
    shape = 3, size = 1.1, aes(color = "Filter"),
    groupOnX = FALSE
  ) +
  geom_point(
    data = results_aggr2[results_aggr2$filter == "Borda", ],
    shape = 19, size = 2, aes(color = "Borda Filter")
  ) +
  facet_wrap(~task.id) +
  scale_color_manual(guide = guide_legend(override.aes = list(shape = c(19, 3))),
                     values = c("Filter" = "#BC8C29FF",
                     "Borda Filter" = "#0072B5FF")) +
  labs(x = "RMSE", y = "Task", colour = NULL) +
  guides(size = FALSE) +
  scale_x_continuous(limits = c(27, 51)) +
  theme_pubr() +
  theme(
    panel.grid.major.y = element_line(size = 0.1, linetype = "dashed"),
    axis.title.y = element_blank(),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 12),
  )
```
